LHC abort gap monitor electronics upgrade

### 2024-04-05 paper.tex
changed caption of the bsra daq picture
existing system picture added to paper

\subsection{Current Solution}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

@@

\subsection{Acquisition System}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\section{}
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{bsra_daq.pdf}
    \caption{upgraded amplifier}
    \label{fig:amplifier}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\subsection{Low band Amplifier}
% \input{tables/system_comparison.tex} 
%compare the changes and comment the expected changes
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{amp_schematics.pdf}
    \caption{upgraded amplifier}
    \label{fig:amplifier}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\subsection{Installation in LHC}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{installation.jpg}
    \caption{installation picture}
    \label{fig:amplifier}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\section{Control Interface}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{control_interface.jpg}
    \caption{installation picture}
    \label{fig:amplifier}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

>>>>

\subsection{Current Solution}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{existing_system_processing.pdf}
    \caption{Current system block diagram}
    \label{fig:current_system_processing}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

@@

\subsection{Acquisition System}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{bsra_daq.pdf}
    \caption{Ackquisition system schematics}
    \label{fig:bsra_daq}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\subsection{Low band Amplifier}
% \input{tables/system_comparison.tex} 
%compare the changes and comment the expected changes
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{amp_schematics.pdf}
    \caption{upgraded amplifier}
    \label{fig:amp_schematics}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\subsection{Installation in LHC}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{installation.jpg}
    \caption{installation picture}
    \label{fig:installation}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

\section{Control Interface}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{control_interface.jpg}
    \caption{installation picture}
    \label{fig:control_interface}
\end{figure}
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
